The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society

### 2023-09-27 manuscript/manuscript.qmd
Update timing plots

p1 <- preds_issue_plot |> 
  mutate(issue_area_nice = factor(
    issue_area_nice, 
    levels = preds_issue_plot_order$issue_area_nice,
    labels = preds_issue_plot_order$issue_area_nice_labels
  )) |> 
  ggplot(aes(x = draw, y = prop)) +
  geom_col(aes(fill = outcome), position = "stack", linewidth = 0, width = 1) +
  geom_text(
    data = preds_issue_text,
    aes(x = 250, y = y_plot, label = prop_ci_nice),
    size = 3, fontface = "bold", color = "white"
  ) +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_fill_manual(values = clrs[c(3, 5, 7)]) +
  facet_wrap(vars(issue_area_nice), strip.position = "bottom", nrow = 1) +
  labs(
    x = NULL, y = "Proportion of predictions", fill = NULL,
    title = "Expected proportion of type of geographic reach across issue area",
    subtitle = "Posterior predictions of outcome categories"
  ) +
  theme_ongo() +
  theme(
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    panel.spacing = unit(5, "pt"),
    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
  )

@@

p1 <- preds_local_plot |> 
  ggplot(aes(x = draw, y = prop)) +
  geom_col(aes(fill = outcome), position = position_stack(), linewidth = 0, width = 1) +
  geom_text(
    data = preds_local_text,
    aes(x = 250, y = y_plot, label = prop_ci_nice),
    size = 3, fontface = "bold", color = "white"
  ) +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_fill_manual(values = clrs[c(3, 5, 7)]) +
  facet_wrap(vars(local_connect), strip.position = "bottom", nrow = 1) +
  labs(
    x = NULL, y = "Proportion of predictions", fill = NULL,
    title = "Expected proportion of type of geographic\nreach across local connections",
    subtitle = "Posterior predictions of outcome categories"
  ) +
  theme_ongo() +
  theme(
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    panel.spacing = unit(5, "pt"),
    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
  )

@@

```{r fig-timing-preds, fig.width=6, fig.height=3}
#| include: true
#| echo: false
#| layout-ncol: 1
#| fig-cap: "Posterior predictions from ordered Beta regression model, conditional on time since registration."
#| fig-subcap: 
#|   - "Proportions of posterior predictions of INGOs working in 1 province, all 32 provinces, or somewhere in between. Distinct x-axis values sum to 100% across the panels."
#|   - "Distribution of the expectation of posterior predictions. These distributions take into account single-province and nationwide predictions and represent the overall conditional average geographic range for INGOs."
preds_timing_plot <- preds_timing |> 
  unnest(preds) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "1 province",
    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
    .prediction == 1 ~ "32 provinces"
  )) |> 
  group_by(outcome, years_since_law, draw) |>  
  summarize(count = n()) |> 
  group_by(years_since_law, draw) |> 
  mutate(prop = count / sum(count))

# preds_timing_plot |>
#   group_by(outcome, years_since_law) |>
#   median_qi(prop)
# 
# epreds_timing |>
#   mutate(.epred = prop_to_provinces(.epred)) |>
#   group_by(years_since_law) |>
#   median_qi(.epred)

ggplot(preds_timing_plot, aes(x = years_since_law, y = prop)) +
  stat_lineribbon(.width = c(0.5, 0.8, 0.95), 
                  alpha = 0.35, fill = clrs[7], color = clrs[7]) +
  facet_wrap(vars(outcome), nrow = 1) +
  scale_y_continuous(labels = label_percent()) +
  labs(x = "Years since law took effect (2017)", 
       y = "Proportion of predictions",
       caption = "Shaded regions show the 50%, 80%, and 95% credible intervals") +
  theme_ongo()

epreds_timing |> 
  ggplot(aes(x = years_since_law, y = .epred)) +
  stat_lineribbon(.width = c(0.5, 0.8, 0.95), 
                  alpha = 0.35, fill = clrs[7], color = clrs[7]) +
  scale_y_continuous(labels = label_percent(),
                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
                                         name = "Expected provinces",
                                         breaks = seq(15, 27, 3))) +
  guides(fill = "none") +
  labs(x = "Years since law took effect (2017)", y = "Expected proportion of provinces",
       caption = "Shaded regions show the 50%, 80%, and 95% credible intervals") +
  theme_ongo() +
  theme(axis.title.y.right = element_text(hjust = 1, margin = margin(l = 10), angle = 90),
        axis.ticks.y.right = element_line(linewidth = 0.25, color = "grey50"))
```

@@

```{r fig-timing-local, fig.width=6, fig.height=3}
#| include: true
#| echo: false
#| fig-cap: "Distribution of the expectation of posterior predictions across both time and local connections. These distributions take into account single-province and nationwide predictions and represent the overall conditional average geographic range for INGOs."
epreds_timing_local |> 
  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |> 
  ggplot(aes(x = years_since_law, y = .epred)) +
  stat_lineribbon(.width = c(0.5, 0.8, 0.95), 
                  alpha = 0.35, fill = clrs[7], color = clrs[7]) +
  scale_y_continuous(labels = label_percent(),
                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
                                         name = "Expected provinces",
                                         breaks = seq(3, 27, 4))) +
  guides(fill = "none") +
  labs(x = "Years since law took effect (2017)", y = "Expected proportion of provinces",
       caption = "Shaded regions show the 50%, 80%, and 95% credible intervals") +
  facet_wrap(vars(local_connect)) +
  theme_ongo() +
  theme(axis.title.y.right = element_text(hjust = 1, margin = margin(l = 10), angle = 90),
        axis.ticks.y.right = element_line(linewidth = 0.25, color = "grey50"))
```

>>>>

p1 <- preds_issue_plot |> 
  mutate(issue_area_nice = factor(
    issue_area_nice, 
    levels = preds_issue_plot_order$issue_area_nice,
    labels = preds_issue_plot_order$issue_area_nice_labels
  )) |> 
  ggplot(aes(x = draw, y = prop)) +
  geom_col(aes(fill = outcome), position = "stack", linewidth = 0, width = 1) +
  geom_text(
    data = preds_issue_text,
    aes(x = 250, y = y_plot, label = prop_ci_nice),
    size = 3, fontface = "bold", color = "white"
  ) +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_fill_manual(values = clrs[c(3, 5, 7)]) +
  facet_wrap(vars(issue_area_nice), strip.position = "bottom", nrow = 1) +
  labs(
    x = NULL, y = "Predicted probability of geographic reach", fill = NULL,
    title = "Predicted proportion of type of geographic reach across issue area",
    subtitle = "Posterior predictions of outcome categories"
  ) +
  theme_ongo() +
  theme(
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    panel.spacing = unit(5, "pt"),
    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
  )

@@

p1 <- preds_local_plot |> 
  ggplot(aes(x = draw, y = prop)) +
  geom_col(aes(fill = outcome), position = position_stack(), linewidth = 0, width = 1) +
  geom_text(
    data = preds_local_text,
    aes(x = 250, y = y_plot, label = prop_ci_nice),
    size = 3, fontface = "bold", color = "white"
  ) +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_fill_manual(values = clrs[c(3, 5, 7)]) +
  facet_wrap(vars(local_connect), strip.position = "bottom", nrow = 1) +
  labs(
    x = NULL, y = "Predicted probability of geographic reach", fill = NULL,
    title = "Predicted proportion of type of\ngeographic reach across local connections",
    subtitle = "Posterior predictions of outcome categories"
  ) +
  theme_ongo() +
  theme(
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    panel.spacing = unit(5, "pt"),
    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
  )

@@

```{r fig-timing-preds, fig.width=8, fig.height=4}
#| include: true
#| echo: false
#| fig-cap: "Posterior predictions from ordered Beta regression model, 
#|   conditional on time since law took effect in January 2017. *Top*: Predicted 
#|   proportion of INGOs working in 1 province, all 32 provinces, or somewhere 
#|   in between. Filled areas depict 50 posterior samples of the outcome category 
#|   probabilities, so the fuzziness represents the uncertainty in category 
#|   boundaries. *Bottom*: Expectation (or average) of posterior predictive 
#|   distributions. This distribution takes into account single-province and 
#|   nationwide predictions and represents the *overall* conditional average 
#|   geographic range for INGOs over time. Shaded regions show the 50%, 80%, 
#|   and 95% credible intervals."
preds_timing_plot <- preds_timing |> 
  unnest(preds) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "Only 1 province",
    .prediction > 0 & .prediction < 1 ~ "Between 1–32 provinces",
    .prediction == 1 ~ "All 32 provinces",
    .ptype = factor(
      levels = c("Only 1 province", "Between 1–32 provinces", "All 32 provinces"), 
      ordered = TRUE)
  )) |> 
  mutate(years_since_law = 2017 + years_since_law) |> 
  group_by(outcome, years_since_law, draw) |>
  summarize(count = n()) |> 
  group_by(years_since_law) |> 
  mutate(prop = count / sum(count) * 100)

preds_timing_text <- preds_timing_plot |> 
  filter(years_since_law == 2017.2) |> 
  group_by(outcome) |> 
  summarize(median_prop = median_qi(prop)) |> 
  unnest(median_prop) |> 
  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
  mutate(y_plot = 1 - y_plot) |> 
  mutate(years_since_law = 2017.2)

layers <- preds_timing_plot |> 
  filter(draw <= 50) |> 
  split(~ draw) |> 
  lapply(\(x) {
    geom_area(
      data = x,
      aes(y = prop, fill = outcome),
      alpha = 0.1
    )
  })

p1 <- ggplot(preds_timing_plot, aes(x = years_since_law)) +
  layers +
  geom_text(
    data = preds_timing_text, 
    aes(y = y_plot, label = outcome),
    color = "white",
    hjust = 0, fontface = "bold", size = 3, show.legend = FALSE
  ) +
  scale_x_continuous(expand = expansion(mult = 0.02)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_color_manual(values = colorspace::darken(clrs[c(3, 5, 7)], 0.1)) +
  scale_fill_manual(values = colorspace::lighten(clrs[c(3, 5, 7)], 0)) +
  labs(
    x = NULL, y = "Predicted probability of geographic reach", fill = NULL,
    title = "Predicted proportion of type of \ngeographic reach since January 2017",
    subtitle = "Posterior predictions of outcome categories"
  ) +
  guides(fill = "none") +
  theme_ongo() +
  theme(
    panel.grid.major = element_blank()
  )

p2 <- epreds_timing |>
  ggplot(aes(x = years_since_law, y = prop_to_provinces(.epred))) +
  stat_lineribbon(
    .width = c(0.5, 0.8, 0.95),
    alpha = 0.35, fill = clrs[6], color = clrs[6]
  ) +
  scale_y_continuous(
    breaks = seq(0, 32, 8),
    sec.axis = sec_axis(
      trans = ~ provinces_to_prop(.),
      name = "Proportion of provinces",
      breaks = seq(0, 1, 0.25),
      labels = label_percent()
    )
  ) +
  labs(
    x = NULL, y = "Expected provinces",
    title = "Expected count of provinces",
    subtitle = "Expectation of posterior predictions"
  ) +
  coord_cartesian(ylim = c(1, 32)) +
  theme_ongo()

p1 | p2
```

@@

```{r fig-timing-local, fig.width=6, fig.height=3, out.width="80%"}
#| include: true
#| echo: false
#| fig-cap: "Expectation (or average) of posterior predictive distributions 
#|   from model with interaction between local connections and time since 
#|   January 2017. These predictions take into account single-province and 
#|   nationwide predictions and represent the overall conditional average 
#|   geographic range for INGOs over time across, conditional on local 
#|   connections. Shaded regions show the 50%, 80%, and 95% credible intervals"
epreds_timing_local |>
  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |>
  ggplot(aes(x = years_since_law, y = prop_to_provinces(.epred))) +
  stat_lineribbon(
    .width = c(0.5, 0.8, 0.95),
    alpha = 0.35, fill = clrs[6], color = clrs[6]
  ) +
  scale_y_continuous(
    breaks = seq(0, 32, 8),
    sec.axis = sec_axis(
      trans = ~ provinces_to_prop(.),
      name = "Proportion of provinces",
      breaks = seq(0, 1, 0.25),
      labels = label_percent()
    )
  ) +
  guides(fill = "none") +
  labs(
    x = NULL, y = "Expected provinces",
    title = "Expected count of provinces across local connections",
    subtitle = "Expectation of posterior predictions"
  ) +
  coord_cartesian(ylim = c(1, 32)) +
  facet_wrap(vars(local_connect)) +
  theme_ongo()
```
